\documentclass[journal]{IEEEtran}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{cite}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{xcolor}

\title{Rendezvous-Aware Route Choice for Urban Ride-Pooling Under Occlusion}
\author{Anonymous Authors}

\begin{document}
\maketitle

\begin{abstract}
This paper studies route choice in urban ride-pooling through route-induced rendezvous opportunities. Instead of valuing a route only by the riders who lie near its corridor, the method values the route by the feasible and observable meeting opportunities it creates. The paper's central claim is that urban occlusion changes route value in a structured way: some common meeting opportunities are easier to coordinate and more reliable than others, so route choice should optimize over feasible and observable rendezvous opportunities rather than proximity alone. The manuscript package on this branch is intentionally separate from earlier route-choice work and is paired only with the \texttt{rendezvous\_*} result namespace.
\end{abstract}

\begin{IEEEkeywords}
ride-pooling, rendezvous, route choice, urban occlusion, meeting-point selection
\end{IEEEkeywords}

\section{Introduction}
Routes expose different sets of common meeting opportunities. In dense urban settings, those opportunities differ not only in accessibility but also in observability and pickup reliability. This paper reframes route choice around that distinction.

\section{Method}
The method compares three route-valuation views: corridor-only exposure, rendezvous feasibility, and observability-aware rendezvous valuation. Meeting opportunities are represented by route anchor cells and evaluated with a proxy-first observability model. The current branch augments NYC TLC demand data with official NYC Centerline, Sidewalk Centerline, Building Footprints, PLUTO, and Elevation Points layers aggregated to H3 to provide a reproducible urban-context signal for occlusion-aware routing.

\section{Experiments}
The primary evidence layer is a controlled single-driver route-choice study. Rolling dispatch is used as a secondary validation layer. The branch writes all paper-facing outputs to the \texttt{results/rendezvous\_*} namespace.

\section{Results}
Populate this section from the outputs generated by \texttt{scripts/run\_rendezvous\_artifact.py}, \texttt{scripts/run\_rendezvous\_dispatch.py}, and \texttt{scripts/summarize\_rendezvous\_results.py}.

\section{Conclusion}
The implementation on this branch is designed to support a publishable paper whose primitive is feasible and observable rendezvous opportunities rather than near-route riders.

\bibliographystyle{IEEEtran}
\bibliography{references}
\end{document}
